DisReserv (v1.0): Analytical displacement solution due to reservoir compaction with arbitrary geometry and under arbitrary pressure changes

### 2020-09-21 manuscript/manuscript-reservoir.tex
include zenodo

\codedataavailability{
The current version of our code is freely distributed under the BSD 3-clause licence and it is available for download at Zenodo: http://doi.org/XXXXXXXX. 
The latest development version of our code can be freely downloaded from a repository on GitHub (https://github.com/pinga-lab/DisReserv). 
Instructions for running  the current version of our code are also provided on the repository.
The code is still being improved and we encourage the user to work with the latest development version. 
The code was developed as an open-source Python language (Python 3.7.6).
The numerical applications were produced in Jupyter Notebook. 
The data of the pore pressure distribution simulating a realistic reservoir 
$(realistic-model.pickle)$ are available  in the  above-mentioned repositories.
} %% use this section when having data sets and software code available

>>>>

\codedataavailability{
The current version of our code is freely distributed under the BSD 3-clause licence and it is available for download at Zenodo: http://doi.org/10.5281/zenodo.4041985 . 
The latest development version of our code can be freely downloaded from a repository on GitHub (https://github.com/pinga-lab/DisReserv). 
Instructions for running  the current version of our code are also provided on the repository.
The code is still being improved and we encourage the user to work with the latest development version. 
The code was developed as an open-source Python language (Python 3.7.6).
The numerical applications were produced in Jupyter Notebook. 
The data of the pore pressure distribution simulating a realistic reservoir 
$(realistic-model.pickle)$ are available  in the  above-mentioned repositories.
} %% use this section when having data sets and software code available
